Unshuffling Permutations

### 2015-09-27 submission.tex
typos

  It is immediate that $\mu$ can be constructed in polynomial-time in $n$ and $k$.
  % We claim that $\sigma$ occurs in $\pi$ if and only if
  % there exists a containment-free perfect matching
  % $\mathcal{M}$ in $K_\mu$ such that
  % for any two disctinct edges
  % $(a, b)$ and $(a', b')$ in $\mathcal{M}$
  % we have $\mu(a) < \mu(a')$ if and only if $\mu(b) < \mu(b')$.
  It can be shown (see Appendix) that
  that $\sigma$ occurs in $\pi$ if and only if
  there exists a containment-free perfect matching
  $\mathcal{M}$ in $K_\mu$ such that
  for any two disctinct edges
  $(a, b)$ and $(a', b')$ in $\mathcal{M}$
  we have $\mu(a) < \mu(a')$ if and only if $\mu(b) < \mu(b')$.
  \qed
\end{proof}

>>>>

  It is immediate that $\mu$ can be constructed in polynomial-time in $n$ and $k$.
  % We claim that $\sigma$ occurs in $\pi$ if and only if
  % there exists a containment-free perfect matching
  % $\mathcal{M}$ in $K_\mu$ such that
  % for any two disctinct edges
  % $(a, b)$ and $(a', b')$ in $\mathcal{M}$
  % we have $\mu(a) < \mu(a')$ if and only if $\mu(b) < \mu(b')$.
  It can be shown (see Appendix) that
  $\sigma$ occurs in $\pi$ if and only if
  there exists a containment-free perfect matching
  $\mathcal{M}$ in $K_\mu$ such that
  for any two disctinct edges
  $(a, b)$ and $(a', b')$ in $\mathcal{M}$
  we have $\mu(a) < \mu(a')$ if and only if $\mu(b) < \mu(b')$.
  \qed
\end{proof}
